Appendix

### 2020-05-01 appendix/appendixV5.Rmd
Table 3. Back to summary. LaTex code.

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: pdf_document
---

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
# str(aux$scoef) -- Obs: this line originally was in the main text. Fix? - LMM
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)

aux = dat %>%
  group_by(depvar2) %>%
  summarise(n = n(),
            mean_coef = mean(coef, na.rm = T),
            median_coef = median(coef, na.rm = T)) %>%
  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
  select(depvar2, n, pct, mean_coef, median_coef)

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)

aux = dat %>%
  group_by(depvar2, year) %>%
  summarise(n = n(),
            mean_coef = round(mean(coef, na.rm = T), digits = 3),
            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
  group_by(year) %>%
  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
  arrange(year) %>%
  rename(Moderator = depvar2,
         Year = year,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef
         )

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

@@

#grid.arrange(f8, f9, f11, 
#             f10,f12, f13,
#             f14,
#             ncol = 2,
#             nrow = 4)
#library(ggplot2)

@@

#ggpubr::ggarrange(plots[[1]],plots[[2]],
#                  plots[[3]],plots[[4]],
#                  plots[[5]],plots[[6]],
#                  plots[[7]],
#                  nrow = 4, ncol = 2
#                  )

#ggpubr::ggarrange(f1,f2, 
#          labels = c("A", "B"),
#          ncol = 1, nrow = 2)

#grid.draw(rbind(f1,f2, size = "first"))

#plot_grid(f1,f2 + rremove("x.text"), 
#          labels = c("A", "B"),
#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
```

@@

mod1 <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod1, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

collapse_rows_dt <- expand.grid(
    Country =sprintf('Country with a long name %s',c('A','B')),
    State =sprintf('State %s',c('a','b')),
    City =sprintf('City %s',c('1','2')),
    District =sprintf('District %s',c('1','2'))) %>% 
  arrange(Country, State, City) %>% 
  mutate_all(as.character) %>%
  mutate(C1 =rnorm(n()),
         C2 =rnorm(n()))

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)
mod

mod1_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod1_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod2 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod2, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod = permutest(mod, progbar = F)
mod

mod2_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod2_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod3 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod3, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)
mod

mod3_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod3_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod4, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod = permutest(mod, progbar = F)
mod

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod4_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod5 <- tibble(
   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod5, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)
mod

mod5_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod5_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod6 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod6, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)
mod

mod6_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod6_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

\newpage

@@

### Summary of Base Models

```{r, echo=F}
aux = bind_rows(
  mod1,
  mod3,
  mod5
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

### Summary of Base Models (Permutation)

```{r,echo=F}

# Table  3  presents  the  meta-regression  results  for  our  restricted  and  extended  samples.   Eachcolumn represents one of the three measures of public spending we discuss in this paper. To reduce the risk of false positives in our analyses, we use permutation tests to calculate significance levelsfor the meta-regressions (Higgins and Thompson 2004).TABLE 3 AROUND HERE: Meta-regression analysis estimating the effect of moderator variables on public expenditure 
#The first two models show the results for public expenditure per capita.  In both the restrictedand the extended samples, we and that models that use푛as an independent variable tend to detect significantly smaller effects when compared to k. This suggests that an additional member in thelower house has a smaller impact on public spending than a member in the upper house. Moreover,
#the results for the extended sample point out that recent studies and larger effects than older ones,and that changing the electoral rules from majoritarian to non-majoritarian increases the effects oflegislature size on per capita expenditure.The third and fourth columns use the logarithm of expenditure per capita as the dependentvariable.   No covariate  is statistically  significant in our  smaller sample,  but two  moderators arenegatively associated with the outcome in our larger study pool.  They both refer to estimationmethods.  Studies that employ panel/fixed effects or regression discontinuity designs (RDDs) havelower coeficients for log expenditure per capita if we take OLS as the reference category

aux = bind_rows(
  mod1_permu,
  mod3_permu,
  mod5_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

### Summary of Models with all coefficients

```{r,echo=F}
aux = bind_rows(
  mod2,
  mod4,
  mod6
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

### Summary of Models with all coefficients (Permutation)

```{r,echo=F}

aux = bind_rows(
  mod2_permu,
  mod4_permu,
  mod6_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

## Theory of Meta Analysis

@@

aux <- tibble(
  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")")
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)

aux <- tibble(
  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

aux <- tibble(
  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=F, warning=F}
mod = permutest(mod, progbar = F)

aux <- tibble(
    ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

>>>>

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

output: pdf_document
---

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

# Table - General

aux <- dat %>%
  group_by(depvar2) %>%
  summarise(n = n(),
            mean_coef = mean(coef, na.rm = T),
            median_coef = median(coef, na.rm = T)) %>%
  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
  select(depvar2, n, pct, mean_coef, median_coef) %>%
  rename(` ` = depvar2,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef)

kable(aux, 
      booktabs = T,
      align = "c",
      linesep ='') %>% 
  kable_styling(c("striped","bordered","scale_down"), position = "center")

@@

#Table: by year

aux <- dat %>%
  group_by(depvar2, year) %>%
  summarise(n = n(),
            mean_coef = round(mean(coef, na.rm = T), digits = 3),
            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
  group_by(year) %>%
  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
  arrange(year) %>%
  rename(` ` = depvar2,
         Year = year,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef
         )

kable(aux, 
      booktabs = T,
      align = "c",
      linesep ='') %>% 
  kable_styling(c("striped","bordered","scale_down"), position = "center")

@@

### PCTGDP x K

@@

@@

@@

mod1 <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

```{r, echo=FALSE}
mod <- permutest(mod, progbar = F)
mod

mod1_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod2 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod <- permutest(mod, progbar = F)
mod

mod2_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod3 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

```{r, echo=FALSE}
mod <- permutest(mod, progbar = F)
mod

mod3_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod <- permutest(mod, progbar = F)
mod

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod5 <- tibble(
   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

```{r, echo=FALSE}
mod <- permutest(mod, progbar = F)
mod

mod5_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

mod5_permu %>%
  select(-model) %>%
  kable(booktabs = T,align = "c",linesep ='') %>%
  kable_styling(c("striped","bordered","scale_down"), position = "center")

@@

mod6 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

```{r, echo=FALSE}
mod <- permutest(mod, progbar = F)
mod

mod6_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs = bind_rows(
  mod1,
  mod2,
  mod3,
  mod4,
  mod5) %>%
  select(` `) %>%
  distinct()

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "Base") %>%
  select(type, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "All Coefs") %>%
  select(type, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"))

@@

\blandscape
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = T,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value"
      )
    ) %>% 
  collapse_rows(
    1:3,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

```
\elandscape

\newpage
## Theory of Meta Analysis

@@

@@

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

@@

@@

```{r, echo=F, warning=F}
permutest(mod, progbar = F)
